Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-16 Manuscript/proof_outline.tex
mention a precise mathlib commit, with date

\todo[inline]{Mention a precise commit of Mathlib}

\todo[inline]{write about sets or types?}

@@

The goal of our contribution is a formalization of the proof of that theorem in {\tt Lean}. Here, we are going to use \leanline{Lean4}, since \leanline{mathlib} \cite{mathlib2020lean}, the mathematical library of \leanline{Lean} has recently been ported to \leanline{Lean4}.
%Subsequently, we aim to make a pull request for the publication of our code in \leanline{mathlib}.
The Kolmogorov extension theorem is on the interface between measure theory and probability theory. Here, we rely on a decent amount of formalized mathematics in the measure-theory part of {\tt mathlib} (outer measures, above all), while not requiring any specific previous formalization of probability theory. (In fact, most of our results are formulated in terms of finite rather than probability measures.)

>>>>

@@

The goal of our contribution is a formalization of the proof of that theorem in {\tt Lean}. We using \leanline{Lean4} and its mathematical library \leanline{mathlib} \cite{mathlib2020lean}\footnote{All references to results in \leanline{mathlib} are accurate for commit {\tt 537e7f030d6df737d728c7c002fb1928f4615afa}, August 22, 2023.}.
The Kolmogorov extension theorem is on the interface between measure theory and probability theory. Here, we rely on a decent amount of formalized mathematics in the measure-theory part of {\tt mathlib} (outer measures, above all), while not requiring any specific previous formalization of probability theory. (In fact, most of our results are formulated in terms of finite rather than probability measures.)
